% Author: David Sanchez-Jacome

\chapter*{Author's merits} \label{sec:merits}
\addcontentsline{toc}{chapter}{Author's merits}

% \begin{noindent}
\section*{Journal publications}

\begin{itemize}
  \item M. B. On, F. Ashtiani, \textbf{D. Sanchez-Jacome}, et al., "Programmable integrated photonics for topological Hamiltonians," \textit{Nat. Commun.}, vol. 15, no. 629, 2024. doi: \href{https://doi.org/10.1038/s41467-024-44939-3}{10.1038/s41467-024-44939-3}.
  \item D. Pérez-López, A. Gutierrez, \textbf{D. Sánchez}, et al., "General-purpose programmable photonic processor for advanced radiofrequency applications," \textit{Nat. Commun.}, vol. 15, no. 1563, 2024. doi: \href{https://doi.org/10.1038/s41467-024-45888-7}{10.1038/s41467-024-45888-7}.
  \item Z. Xie, \textbf{D. Sánchez-Jácome}, L. Torrijos-Morán, and D. Pérez-López, "Software-defined optical networking applications enabled by programmable integrated photonics," \textit{J. Opt. Commun. Netw.}, vol. 16, pp. D10-D17, 2024. doi: \href{https://doi.org/10.1364/JOCN.521505}{10.1364/JOCN.521505}.
  \item I. Teofilovic, A. Cem, \textbf{D. Sanchez-Jacome}, D. Pérez-López and F. Da Ros, "Thermal Crosstalk Modelling and Compensation Methods for Programmable Photonic Integrated Circuits," in
    \textit{Journal of Lightwave Technology}, vol. 42, no. 22, pp. 7816-7824, 15 Nov.15, 2024, doi: \href{https://doi.org/10.1109/JLT.2024.3430504}{10.1109/JLT.2024.3430504}.
  \item A. Tsirigotis, A. Sarantoglou, S. Deligiannidis, E. Sánchez, \textbf{D. Sanchez}, et al., "Photonic neuromorphic accelerator for convolutional neural networks based on an integrated
    reconfigurable mesh," \textit{Nat. Commun. Eng.}, vol. 4, no. 80, 2025. \href{https://doi.org/10.1038/s44172-025-00416-3}{10.1038/s44172-025-00416-3}.
\end{itemize}

\section*{Conference contributions}

\begin{itemize}
  \item \textbf{D. Sanchez-Jacome}, M. Rodriguez-Losada, E. Sanchez-Gomaris, and D. Perez-Lopez, “Parametric Unitary Operators Experimentally Demonstrated on a Software-Defined Photonic Integrated Processor,” in \textit{2024 European Conference of Optical Communications (ECOC24)}, 2024.
  \item Z. Xie, \textbf{D. Sanchez-Jacome}, L. Torrijos-Moran, and D. Perez-Lopez, “Reconfigurable on-chip optical circuit switch for software-defined networking applications,” in \textit{2024 European Conference of Optical Communications (ECOC24)}, 2024.
  \item A. Tsirigotis, \textbf{D. Sanchez-Jacome}, et al., “Experimental Investigation of a Neuromorphic Accelerator based on Reconfigurable Photonic Chip for High-Speed Image Processing,” in \textit{2024 European Conference of Optical Communications (ECOC24)}, 2024.
  \item A. Cem, \textbf{D. Sanchez-Jacome}, D. Pérez-López, and F. Da Ros, "Thermal Crosstalk Modeling and Compensation for Programmable Photonic Processors," in \textit{2023 IEEE Photonics Conference (IPC)}, Orlando, FL, USA, 2023, pp. 1-2. doi: \href{https://doi.org/10.1109/IPC57732.2023.10360567}{10.1109/IPC57732.2023.10360567}.
  \item \textbf{D. Sánchez-Jácome}, A. Santome-Valverde, and D. Pérez-López, “Programmable Integrated Photonics Circuits: Applications for 5G, Computing, Data Center, Sensing, and Beyond,” in
    \textit{2022 Epixfab Silicon Photonics Summer School}, 2022. \textbf{Received the best poster award}.
  \item D. Pérez-López, A. López Hernández, M. Gutiérrez, \textbf{D. Sánchez-Jacome}, and E. Sánchez, “Dynamically-reconfigurable Photonic Integrated Circuits and Its Control Algorithms,” in \textit{2023 Conference on Lasers and Electro-Optics (CLEO)}, 2023.
  \item \textbf{D. Sánchez-Jácome}, M. Gutiérrez-Zubillaga, Z. Xie, and D. Pérez-López, “Software-defined Synthesis of Optical Circuits on a Programmable Photonic Platform,” in \textit{2023 IEEE Society for Photonics Summer Topics Meeting Series (SUM)}, 2023.
  \item F. Ashtiani, M. B. On, \textbf{D. Sanchez-Jacome}, D. Perez-Lopez, S. J. Ben Yoo, and A. Blanco-Redondo, “Photonic Max-Pooling for Deep Neural Networks Using a Programmable Photonic Platform,” in \textit{Optical Fiber Communication Conference (OFC) 2023}, 2023, paper M1J.6.
\end{itemize}

\section*{Patents}

\begin{itemize}
  \item L. Torrijos-Morán, D. Pérez-López, T. Hoekstra, \textbf{D. Sánchez-Jácome}, and J. Fernández-Vicente, “Optical Networking Device,” submitted to European Patent Office.
\end{itemize}
% \end{noindent}
